---
title: "Final project"
author: "Owen Jones"
date: "4/21/2021"
output: html_document
---
```{r}
library('tidyverse')
library('anytime')
```

**1**
Our final project is on the data set CAB_RIDES: investigating the relationship between distance and price. Later on, we will explore how this relationship is affected by the variables cab_type and name. 

```{r}
cab_rides<-read.csv('https://raw.githubusercontent.com/objones25/Final_Project_QTM_150/master/CAB_RIDES.csv')
```

**2**
Our response variable will be price because we want to determine the effect that the variable time_stamp has on the variable price.

```{r}
summary(cab_rides$price)
```
**3**
The distribution of prices is very right skewed. Outliers are considered values above 1.5*IQR + 3Q. 5143 NA's and outliers were removed from the data set 
```{r}
ggplot(data = cab_rides)+geom_boxplot(mapping = aes(y = 0, x = price), outlier.shape = NA, na.rm = T)
ggplot(data = cab_rides)+geom_histogram(mapping = aes(x = price), binwidth = 1, na.rm = T)
cab_subset<-subset(cab_rides, price < 1.5*IQR(price, na.rm = T) + quantile(price, 0.75, na.rm = T))
```

**4**
We chose time_stamp as our explanatory variable.
```{r}
ggplot(data = cab_subset)+geom_histogram(mapping = aes(x = distance), binwidth = 0.01, na.rm = T)
```

**5**
